A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-11-28 writeup/revision 1/paper.tex
Cropped map
Updated paper

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skill claims by measuring their ability to correctly translate words, and by geolocating workers to see if they reside in countries where the languages are likely to be spoken. Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 100 languages.  Our study ran for several months, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilingual workers would complete it.  Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.  We use this data to recommend languages with the largest speaker populations as good candidates for other researchers who want to  develop crowdsourced, multilingual technologies.

@@

@@

While the demographics reported are likely to shift overtime, as Amazon expands its methods of payments and reaches new countries, the data presented provides a valuable snapshot of the current state of MTurk, and the methods used can be applied generally in future research.

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/map.png}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  4,983 workers in our study.  Omitted are 60 workers who were located in more than one country during the study, and 238 workers who could not be geolocated. The size of the circles represents the number of workers from each country.  The two largest are India (1,998 workers) and the United States (866).  To calibrate the sizes: the Philippines has 142 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Background and Related Work}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost, workforce. MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called `Human Intelligence Tasks' (HITs).  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhnThesis,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

Several researchers have investigated using MTurk to build bilingual parallel corpora for machine translation, a task which stands to benefit low cost, high volume  translation on demand \cite{Germann2001}.  \newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese, Hindi, Telugu, Urdu, and Haitian Creole.  In a study of 2000 Urdu sentences, 
\newcite{zaidan-callisonburch:2011:ACL-HLT2011a} presented methods for achieving professional-level translation quality from Turkers by soliciting multiple English translations of each foreign sentence. 
\newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100 times more Modern Standard Arabic-English parallel data.

@@

We drew our data from the different language versions of Wikipedia.   We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} (Table \ref{wikipedia-buckets}). For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them. The resulting vocabularies served as the input to our translation HIT.

@@

\hline
\end{tabular}
\end{center}
\normalsize
\caption{A list of the languages that were used in our study, grouped by the number of Wikipedia articles in the language.  Each language's code is given in parentheses.  These language codes are used in other figures throughout this paper.}\label{wikipedia-buckets}
\end{table}%

@@

The task paid \$0.15 for the translation of 10 words.  
Each set of 10 words was independently translated by three separate workers.  5,281 workers completed 256,604 translations assignments, totaling more than 3 million words, over a period of three and a half months.

@@

\paragraph{Gold standard translations} 
A set of gold standard translations were automatically harvested from Wikipedia  for every language to use as embedded controls. We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign article's title.  To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology  \cite{miller1995wordnet}, (2) either article title was longer than a single word, (3) the English wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\textwidth]{figures/tamil.pdf}
  \begin{tabular}{l}
    \hline
    In March 15,2007 Wiki got a place in Oxford English dictionary. \\
    On March 15, 2007 wiki was included in the Oxford English
    dictionary. \\
    ON MARCH 15, 2007, WIKI FOUND A PLACE IN THE OXFORD ENGLISH
    DICTIONARY \\
    March 15, 2007 oxford english index of wiki's place. \\ \\

  \end{tabular}
  \caption{An example of the variance in translation quality for the
    human translations of a Tamil sentence; the formatting of the
    translations has been preserved exactly.}
  \label{figure:variance}
\end{figure*}

\paragraph{Full sentence translations}
In addition to the bilingual dictionaries, we are interested in Turkers' ability to translate complete sentences. Because the Indian subcontinent is so well represented among our workers, we chose six Indian languages for which to gather translations of full sentences. We selected Bengali, Malyalam, Hindi, Tamil, Telugu, and Urdu as good candidates for our study : these languages have large native speaker populations and are well represented on Wikipedia but they are currently not covered by any professionally translated corpora.

Each of the sentence translation HITs contained ten sequential sentences from a source-language Wikipedia article and asked the worker to enter a free-form translation for each.  We collected four translations from different translators for each source sentence.  Workers were paid \$0.70 per HIT.

Since there is no gold-standard data available for our chosen languages, and it could not be mined in a straight-forward way as in the single word case, we were unable to embed controls into our HITs. We instead accepted or rejected translations based on a review of each worker's submissions, which included a comparison of the translations to a monotonic gloss (produced with a dictionary), and metadata such as the amount of time the worker took to complete the HIT and their geographic location.

Figure~\ref{figure:variance} contains some hand-picked examples of the sorts of translations we obtained. While the lack of a gold-standard data set prevented us from evaluating the collected translations in terms of BLEU scores, as in \newcite{zaidan-callisonburch:2011:ACL-HLT2011a}, we evaluate the quality of the data by using it to train an SMT system. We present results in section \ref{sec:data-analysis}.

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=\linewidth]{figures/quality_bar.pdf}
\caption{Translation quality for languages with at least 50 Turkers.  The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms. Error bars show the 95\% confidence intervals for each language.}
\label{hitlangqual} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Since computing overall quality for a language as the average assignment quality score is biased towards a small number of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
\begin{align}	
	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}\text{Quality}(a_j)}}{\mid \texttt{assigns[$i$]} \mid}
\end{align}	
where \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.

Quality for a language is then given by
\begin{align}	
	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}\text{Quality}(t_j)}}{\mid \texttt{turkers[$i$]} \mid}
\end{align}	
When a Turker completed assignments in more than one language, their quality was computed separately for each language. Figure \ref{hitlangqual} shows the translation quality for languages with contributions from at least 50 workers.

\paragraph{Use of machine translation}

One obvious way for dishonest workers to shortcut is to use available online translation tools. Although we followed best practices to deter copying-and-pasting into online MT systems  by  rendering words and sentences as images \cite{zaidan-callisonburch:2011:ACL-HLT2011a}, this strategy does not prevent workers from typing the words into an MT system if they are able to type in the language's script.

We quantified each Turker's overlap with the Google translations so that we could identify and remove workers that appeared to be misusing Google Translate. We used Google to translate all 10,000 words for the 51 foreign languages that Google Translate covered at the time of the study. We measured the percent of workers' translations that exactly matched the translation returned from Google.

@@

%%%%%%%%%%%%%%% GOOGLE OVERLAP BAR %%%%%%%%%%%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=1\linewidth]{figures/google_bar.png}
%\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.37.}
%\label{googlematch} 
%\end{center}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

We found that while overall overlap is high (the average Turker's overlap was 41\%), it is not consistently high across all Turkers. Figure \ref{dist} shows that while a small number of Turkers have a very high amount of overlap with Google (near 80\%) the majority overlap less than half of the time. It seems likely that those with very high overlap are cheating, but it is also reasonable to assume that honest Turkers will overlap with Google with some regularity. We divide the workers into three groups: those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, e.g. submitting random text).

Our controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate. We therefore remove the 500 Turkers with the highest overlap with Google. This equates to removing all workers with greater than 70\% overlap. Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.

@@

\begin{figure}[h!]
\centering
\begin{subfigure}[b]{\linewidth}
%\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.png}
\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.pdf}
\caption{Individual Turker overlap with Google Translate. We remove the 500 workers with the highest overlap (shaded region on the left) from our analysis, as it is reasonable to assume these workers are cheating by submitting translations from Google. We believe the workers with no overlap (shaded region on the right) are also likely to be cheating, e.g. by submitting random text, and we target these workers through our embedded quality controls.}                
\label{dist}
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
%\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.png}
\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.pdf}
\caption{Cumulative distribution of overlap with Google translate for workers and translations. We see that eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
\label{cdf}
\end{subfigure}
\caption{}\label{cheaters}
\end{figure}

@@

We performed an analysis of our data to address the following questions:
\begin{itemize}
\item How quickly can we expect work to be completed in a particular language? 
\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
\item Are our gold standard translations valid? 
\item Can Turkers' translations be used to train an MT system? 
\end{itemize}

\paragraph{Speed of completion}

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{table*}
\scriptsize
\begin{center}
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi & 0.635 (296) & \textbf{0.695} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil & \textbf{0.653} (273) * & 0.250 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
Malayalam & 0.764 (234) & \textbf{0.827} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
Spanish & 0.814 (191) & \textbf{0.837} (18) & US (122) Mexico (16) Spain (14)  & India (15) Newzealand (1) Brazil (1) \\
French & 0.750 (170) & \textbf{0.816} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
Chinese & \textbf{0.601} (116) & 0.552 (21) & US (75) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
German & \textbf{0.825} (91) & 0.768 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
Italian & \textbf{0.863} (90) & 0.796 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
Amharic & \textbf{0.136} (16) * & 0.009 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
Kannada & 0.704 (105) & NA (0) & India (105)  & \\
Arabic & \textbf{0.741} (60) * & 0.604 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
Sindhi & \textbf{0.190} (96) & 0.062 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
Portuguese & 0.869 (101) & \textbf{0.963} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
Turkish & 0.759 (76) & \textbf{0.804} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
Telugu & \textbf{0.799} (102) & 0.500 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
Irish & \textbf{0.742} (54) & 0.709 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
Swedish & \textbf{0.734} (54) & 0.711 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
Czech & \textbf{0.706} (45) & 0.612 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
Russian & \textbf{0.146} (67) & 0.119 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
Breton & 0.167 (3) & \textbf{0.178} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
\hline\hline
\end{tabular}
\normalsize
\end{center}
\caption{Translation quality when partitioning the translations into two groups, one containing translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other containing translations from Turkers outside those regions. In general, in-region Turkers provide higher quality translations. (*) indicates differences significant at p=0.05.} \label{region-summary}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\paragraph{Validation of controls} 
Higher overlap with Google Translate corresponds slightly to higher quality scores (Pearson $\rho$ = 0.27), suggesting that some control translations have already been indexed by Google. We therefore investigated the validity of our use of Wikipedia inter-language links as gold standard translations.

As an extrinsic measure of translation quality, we measure the proportion of $<${\it word, translation}$>$ pairs received from Mechanical Turk which appear in external dictionaries.  We had external bilingual dictionaries for 24 of the 100 languages examined in this study.\footnote{The bilingual dictionaries were between English and az, bg, bn, bs, cy, es, fa, hi, id, lv, ms, ne, pl, ro, ru, sk, so, sq, sr, ta, tr, uk, ur, and uz. }  We used each of these bilingual dictionaries to compute language-level quality scores, using the dictionary's translation as a gold standard translation for any of the 10,000 foreign words in our study.  In some cases, the overlap of words was low, since dictionaries list root forms of words and we translated inflected forms.

We ranked the 24 languages based on their translation quality scores according to the external dictionaries, and calculated correlation when compared to the ranking produced by our gold standard control.  The Pearson correlation was $\rho=0.53$.  We computed a correlation coefficient of $\rho=0.37$ for ranking of the translation quality of individual Turkers using the two sources of reference translations.

Given the strong positive correlation, we are satisfied that the trends reported in this paper hold when using either our gold standard translations or external bilingual dictionaries.

>>>>

\begin{abstract}
We present a large scale study of the languages spoken by bilingual workers on Mechanical Turk (MTurk).  
We establish a  methodology for determining the language skills of anonymous crowd workers that is more robust than simple surveying.  We validate workers' self-reported language skill claims by measuring their ability to correctly translate words, and by geolocating workers to see if they reside in countries where the languages are likely to be spoken. Rather than posting a one-off survey, we posted paid tasks consisting of 1,000 assignments to translate a total of 10,000 words in each of 100 languages.  Our study ran for several months, and was highly visible on the MTurk crowdsourcing platform, increasing the chances that bilingual workers would complete it.  Our study was useful both to create bilingual dictionaries and to act as census of the bilingual speakers on MTurk.  We use this data to recommend languages with the largest speaker populations as good candidates for other researchers who want to  develop crowdsourced, multilingual technologies. To further demonstrate the value of creating data via crowdsourcing, we hire workers to create bilingual parallel corpora in six Indian languages, and use them to train statistical machine translation systems.

@@

%%%%%%%%%%%%%%% MAP OF WORKER LOCATIONS %%%%%%%%%%%
\begin{figure*}[h]
\centering
\includegraphics[width=\linewidth]{figures/map.pdf}
\caption{The number of workers per country.  This map was generated based on geolocating the IP address of  4,983 workers in our study.  Omitted are 60 workers who were located in more than one country during the study, and 238 workers who could not be geolocated. The size of the circles represents the number of workers from each country.  The two largest are India (1,998 workers) and the United States (866).  To calibrate the sizes: the Philippines has 142 workers, Egypt has 25, Russia has 10, and Sri Lanka has 4.}
\label{map}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\section{Background and Related Work}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost workforce. MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called `Human Intelligence Tasks' (HITs).  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhnThesis,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

Several researchers have investigated using MTurk to build bilingual parallel corpora for machine translation, a task which stands to benefit low cost, high volume  translation on demand \cite{Germann2001}.  \newcite{ambati_act} conducted a pilot study by posting 25 sentences to MTurk for Spanish, Chinese, Hindi, Telugu, Urdu, and Haitian Creole.  In a study of 2000 Urdu sentences, 
\newcite{zaidan-callisonburch:2011:ACL-HLT2011a} presented methods for achieving professional-level translation quality from Turkers by soliciting multiple English translations of each foreign sentence. 
\newcite{Zbib-etal:2012:NAACL} used crowdsourcing to construct a 1.5 million word parallel corpus of dialect Arabic and English, training a statistical machine translation system that produced higher quality translations of dialect Arabic than a system a trained on 100 times more Modern Standard Arabic-English parallel data. \newcite{zbib-EtAl:2013:NAACL-HLT} conducted a systematic study that showed that training an MT system on crowdsourced translations resulted in the same performance as training on professional translations, at $\frac{1}{5}$ the cost.
\newcite{Hu:2010,Hu:2011} performed crowdsourced translation by having monolingual speakers collaborate and iteratively improve MT output.

@@

We drew our data from the different language versions of Wikipedia.   We selected the 100 languages with the largest number of articles,\footnote{\url{http://meta.wikimedia.org/wiki/List_of_Wikipedias}} (Table \ref{Wikipedia-buckets}). For each language, we chose the 1,000 most viewed articles over a 1 year period,\footnote{\url{http://dumps.wikimedia.org/other/pagecounts-raw/}} and extracted the 10,000 most frequent words from them. The resulting vocabularies served as the input to our translation HIT.

@@

\hline
\end{tabular}
\end{center}
\normalsize
\caption{A list of the languages that were used in our study, grouped by the number of Wikipedia articles in the language.  Each language's code is given in parentheses.  These language codes are used in other figures throughout this paper.}\label{Wikipedia-buckets}
\end{table}%

@@

The task paid \$0.15 for the translation of 10 words.  
Each set of 10 words was independently translated by three separate workers.  5,281 workers completed 256,604 translation assignments, totaling more than 3 million words, over a period of three and a half months.

@@

\paragraph{Gold standard translations} 
A set of gold standard translations were automatically harvested from Wikipedia  for every language to use as embedded controls. We used Wikipedia's inter-language links to pair titles of English articles with their corresponding foreign article's title.  To get a more translatable set of pairs, we excluded any pairs where: (1) the English word was not present in the WordNet ontology  \cite{miller1995wordnet}, (2) either article title was longer than a single word, (3) the English Wikipedia page was a subcategory of person or place, or (4) the English and the foreign titles were identical or a substring of the other.

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=1.05\linewidth]{figures/hindi.pdf}
  \footnotesize
  \begin{tabular}{p{\linewidth}}
    \hline
In retribution pakistan also did six nuclear tests on 28 may 1998.\\
On 28 May Pakistan also conducted six nuclear tests as an act of redressal.\\
Retaliating on this 'Pakistan' conducted Six(6) Nuclear Tests on 28 May, 1998.\\
pakistan also did 6 nuclear test in retribution on 28 may, 1998 \\ \\
  \end{tabular}
  \normalsize
  \caption{An example of the Turkers' translations of a Hindi sentence. The translations are unedited and contain fixable spelling, capitalization and grammatical errors.}
  \label{figure:variance}
\end{figure}

%%%%%%%%%%%%%%% HITLANG QUALITY BAR %%%%%%%%%%%
\begin{figure*}[h]
\begin{center}
\includegraphics[width=.7\linewidth]{figures/quality_bar.pdf}
\caption{Translation quality for languages with at least 50 Turkers. The dark blue bars indicate the proportion of translations which exactly matched gold standard translations, and light blue indicate translations which were judged to be correct synonyms. Error bars show the 95\% confidence intervals for each language.}
\label{hitlangqual} 
\end{center}
\end{figure*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\paragraph{Full sentence translations}
To demonstrate the feasibility of using crowdsourcing to create multilingual technologies, we hire Turkers to construct bilingual parallel corpora from scratch for six Indian languages.  \newcite{Germann2001} attempted to build a Tamil-English translation system from scratch by hiring professional translators, but found the cost prohibitive. We created parallel corpora by translating the 100 most viewed Wikipedia pages in Bengali, Malyalam, Hindi, Tamil, Telugu, and Urdu into English.  We collected four translations from different Turkers for each source sentence.

%Embedding gold-standard translations into our full-sentence translation HITs was problematic for two reasons: (1) few public bilingual parallel corpora exist for our chosen languages, and (2) Google could have trained its translation system on them already, resulting in high quality translations when Turkers used MT to translate the gold standard sentences. and it could not be mined in a straight-forward way as in the single word case, we were unable to embed controls into our HITs. 
Workers were paid \$0.70 per HIT to translate 10 sentences.  
 We  accepted or rejected translations based on a manual review of each worker's submissions, which included a comparison of the translations to a monotonic gloss (produced with a dictionary), and metadata such as the amount of time the worker took to complete the HIT and their geographic location.

Figure~\ref{figure:variance} shows an example of the translations we obtained. The lack of a professionally translated reference sentences prevented us from doing a systematic comparison between the quality of profession and non-professional translations as  \newcite{zaidan-callisonburch:2011:ACL-HLT2011a} did. Instead we evaluate the quality of the data by using it to train SMT systems. We present results in section \ref{sec:data-analysis}.

@@

Since computing overall quality for a language as the average assignment quality score is biased towards a small number of highly active Turkers, we instead report language quality scores as the average per-Turker quality, where a Turker's quality is  the average quality of all the assignments that she completed:
\begin{align}	
	\text{Quality}(t_i) = \frac{\sum_{a_j \in \texttt{assigns[$i$]}}\text{Quality}(a_j)}{\mid \texttt{assigns[$i$]} \mid}
\end{align}	
where \texttt{assigns[$i$]} is the assignments completed by Turker $i$, and Quality($a$) is as above.

Quality for a language is then given by
\begin{align}	
	\text{Quality}(l_i) = \frac{\sum_{t_j \in \texttt{turkers[$i$]}}\text{Quality}(t_j)}{\mid \texttt{turkers[$i$]} \mid}
\end{align}	
When a Turker completed assignments in more than one language, their quality was computed separately for each language. Figure \ref{hitlangqual} shows the translation quality for languages with contributions from at least 50 workers.

\paragraph{Cheating using machine translation}

One obvious way for workers to cheat is to use available online translation tools. Although we followed best practices to deter copying-and-pasting into online MT systems  by  rendering words and sentences as images \cite{zaidan-callisonburch:2011:ACL-HLT2011a}, this strategy does not prevent workers from typing the words into an MT system if they are able to type in the language's script.

To identify and remove workers who appeared to be cheating by using Google Translate, we calculated each worker's overlap with the Google translations. We used Google to translate all 10,000 words for the 51 foreign languages that Google Translate covered at the time of the study. We measured the percent of workers' translations that exactly matched the translation returned from Google.

@@

%%%%%%%%%%%%%%% GOOGLE OVERLAP BAR %%%%%%%%%%%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=1\linewidth]{figures/google_bar.pdf}
%\caption{Average proportion of Turker translations matching GoogleTranslate, per assignment. Overall average overlap was 0.37.}
%\label{googlematch} 
%\end{center}
%\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{figure}[h!]
\centering
\begin{subfigure}[b]{\linewidth}
%\includegraphics[width=\textwidth]{figures/turker-googmatch-distribution.pdf}
\includegraphics[width=\linewidth]{figures/turker-googmatch-distribution.pdf}
\caption{Individual workers' overlap with Google Translate. We removed the 500 workers with the highest overlap (shaded region on the left) from our analyses, as it is reasonable to assume these workers are cheating by submitting translations from Google. Workers with no overlap (shaded region on the right) are also likely to be cheating, e.g. by submitting random text. }
%, and we target these workers through our embedded quality controls.}                
\label{dist}
\end{subfigure}
\begin{subfigure}[b]{\linewidth}
%\includegraphics[width=\textwidth]{figures/google-cdf-googlangs.pdf}
\includegraphics[width=\linewidth]{figures/google-cdf-googlangs.pdf}
\caption{Cumulative distribution of overlap with Google translate for workers and translations. We see that eliminating all workers with \textgreater 70\% overlap with google translate still preserves 90\% of translations and \textgreater 90\% of workers.}
\label{cdf}
\end{subfigure}
\caption{}\label{cheaters}
\end{figure}

%We found that while overall overlap is high (the average worker's overlap was 41\%), it is not consistently high across all workers. 
Figure \ref{dist} shows overlap between Turkers's translations and Google Translate.  When overlap is high, it seems likely that those with very high overlap are cheating.  It is also reasonable to assume that honest workers will overlap with Google some amount of the time as Google's translations are usually accurate. We divide the workers into three groups: those with very high overlap with Google (likely cheating by using Google to translate words), those with reasonable overlap, and those with no overlap (likely cheating by other means, for instance, by submitting random text).

Our gold-standard controls are designed to identify workers that fall into the third group (those who are spamming or providing useless translations), but they will not effectively flag workers who are cheating with Google Translate. We therefore remove the 500 Turkers with the highest overlap with Google. This equates to removing all workers with greater than 70\% overlap. Figure \ref{cdf} shows that removing workers at or above the 70\% threshold retains 90\% of the collected translations and over 90\% of the workers.

@@

%%%%%%%%%%%%%%% TURKER QUAL SUMMARY TABLE %%%%%%%%%%%
\begin{table*}
\scriptsize
\begin{center}
\begin{tabular}{lllll}
\hline\hline
&\multicolumn{2}{c}{Avg. Turker quality (\# Ts)}&Primary locations&Primary locations\\
&In region&Out of region&of Turkers in region&of Turkers out of region\\
\hline\hline
Hindi & 0.64 (296) & \textbf{0.70} (7) & India (284) UAE (5) UK (3)  & Saudi Arabia (2) Russia (1) Oman (1) \\
Tamil & \textbf{0.65} (273) * & 0.25 (2) & India (266) US (3) Canada (2)  & Tunisia (1) Egypt (1)  \\
Malayalam & 0.76 (234) & \textbf{0.83} (2) & India (223) UAE (6) US (3)  & Saudi Arabia (1) Maldives (1) \\
Spanish & 0.81 (191) & \textbf{0.84} (18) & US (122) Mexico (16) Spain (14)  & India (15) Newzealand (1) Brazil (1) \\
French & 0.75 (170) & \textbf{0.82} (11) & India (62) US (45) France (23)  & Greece (2) Netherlands (1) Japan (1) \\
Chinese & \textbf{0.60} (116) & 0.55 (21) & US (75) Singapore (13) China (9)  & Hongkong (6) Australia (3) Germany (2)  \\
German & \textbf{0.83} (91) & 0.77 (41) & Germany (48) US (25) Austria (7)  & India (34) Netherlands (1) Greece (1)  \\
Italian & \textbf{0.86} (90) & 0.80 (42) & Italy (42) US (29) Romania (7)  & India (33) Ireland (2) Spain (2)  \\
Amharic & \textbf{0.14} (16) * & 0.01 (99) & US (14) Ethiopia (2)  & India (70) Georgia (9) Macedonia (5)  \\
Kannada & 0.70 (105) & N/A (0) & India (105)  & \\
Arabic & \textbf{0.74} (60) * & 0.60 (45) & Egypt (19) Jordan (16) Morocco (9)  & US (19) India (11) Canada (3)  \\
Sindhi & \textbf{0.19} (96) & 0.06 (9) & India (58) Pakistan (37) US (1)  & Macedonia (4) Georgia (2) Indonesia (2)  \\
Portuguese & 0.87 (101) & \textbf{0.96} (3) & Brazil (44) Portugal (31) US (15)  & Romania (1) Japan (1) Israel (1) \\
Turkish & 0.76 (76) & \textbf{0.80} (27) & Turkey (38) US (18) Macedonia (8)  & India (19) Pakistan (4) Taiwan (1) \\
Telugu & \textbf{0.80} (102) & 0.50 (1) & India (98) US (3) UAE (1)  & Saudi Arabia (1)  \\
Irish & \textbf{0.74} (54) & 0.71 (47) & US (39) Ireland (13) UK (2)  & India (36) Romania (5) Macedonia (2)  \\
Swedish & \textbf{0.73} (54) & 0.71 (45) & US (25) Sweden (22) Finland (3)  & India (23) Macedonia (6) Croatia (2)  \\
Czech & \textbf{0.71} (45) & 0.61 (50) & US (17) Czech Republic (14) Serbia (5)  & Macedonia (22) India (10) UK (5)  \\
Russian & \textbf{0.15} (67) & 0.12 (27) & US (36) Moldova (7) Russia (6)  & India (14) Macedonia (4) UK (3)  \\
Breton & 0.17 (3) & \textbf{0.18} (89) & US (3)  & India (83) Macedonia (2) China (1) \\
\hline\hline
\end{tabular}
\normalsize
\end{center}
\caption{Translation quality when partitioning the translations into two groups, one containing translations submitted by Turkers whose location is within regions that plausibly speak the foreign language, and the other containing translations from Turkers outside those regions. In general, in-region Turkers provide higher quality translations. (*) indicates differences significant at p=0.05.} \label{region-summary}
\end{table*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

We performed an analysis of our data to address the following questions:
\begin{itemize}
\item Do workers accurately represent their language abilities?  Should we constrain tasks by region? 
\item How quickly can we expect work to be completed in a particular language? 
%\item Are our gold standard translations valid? 
\item Can Turkers' translations be used to train MT systems? 
\item Do our dictionaries improve MT quality?
\end{itemize}

@@

\paragraph{Speed of translation}

Figure \ref{figure:volume-of-data-by-language} gives the throughput of the full-sentence translation task for the six Indian languages.  The fastest language was Malayalam, for we collected half a million words of translations in just under a week.  Table \ref{table:data-size} gives the size of the data set that we created for each of these languages.

\begin{figure}[t]
  \includegraphics[width=\linewidth]{figures/volume}
  \caption{The total volume of translations (measured in English words)
    as a function of elapsed days. }
  \label{figure:volume-of-data-by-language}
\end{figure}

\begin{table}[t]
  \centering
  \small
  \begin{tabular}{l|rrr}
    		 & sentence   &  English + & dictionary  \\
    language &  pairs  & foreign words &  entries \\
    \hline\hline
    Bengali & 22k & 732k   & 22k \\
    Hindi   &  40k & 1,488k & 22k \\
    Malayalam & 32k & 863k & 23k \\
    Tamil & 38k & 916k & 25k \\
    Telugu & 46k & 1,097k & 21k \\
    Urdu & 35k & 1,356k & 20k \\
  \end{tabular}
  \caption{Size of parallel corpora and bilingual dictionaries collected for each language. }
  \label{table:data-size}
\end{table}
